### 2020-02-06 Literature Review/Literature Review - Revised/sections/DynMARL.tex
minor edits

    \begin{itemize}
        \item Asymmetric games, in which agents have different payoffs, introducing heterogeneity
        and competition into the system.
        \item Stateful Games.
        \item Heterogeneous populations, in which there are p different populations of agents.
    \end{itemize}

@@

    Here lies the opportunity to extend the work of Tuyls' et al. \cite{Tuyls2006AnGames} towards
    continuous action spaces. This would be particularly useful for most robotic applications, which
    operate in continuous spaces.

    Work has commenced in this area, but is still in its infancy. Notable examples are: 
    \cite{Letcher2019DifferentiableMechanics}, in which Letcher et al. consider the dynamics of
    Differentiable Games, though their focus is on its application to gradient descent in GANs as
    opposed to reinforcement learning, and \cite{Galstyan2013}, in which the dynamics of Q-Learning,
    with a Boltzmann action selection is considered. To achieve the result, the author replaces the
    strategy vector with a probability density function (pdf) over the strategy space, which leads
    to an integro-differential equation which describes the evolution of the pdf with time. Due to
    its complexity, the dynamics cannot be analysed as easily as those in \cite{Tuyls2006AnGames},
    and so Galstyan restricts the analysis to the steady-state solution (i.e. the fixed point) of
    the dynamics. Their analysis shows strong agreement with the designed experiments, under varying
    payoff conditions (note that the payoffs are now a function, rather than a discrete matrix).

@@

@@

>>>>

    \begin{itemize}
        \item Asymmetric games, in which agents have different
          payoffs, introducing heterogeneity and competition into the
          system. \fr{this is not really a problem  in relation with swarms, is it?}
        \item Stateful Games. \fr{what is the interest of stateful games?}
        \item Heterogeneous populations, in which there are p different populations of agents.
    \end{itemize}

@@

    Here lies the opportunity to extend the work of Tuyls' et
    al. \cite{Tuyls2006AnGames} towards continuous action spaces. This
    would be particularly useful for most robotic applications, which
    operate in continuous spaces. \fr{do we have other examples?}

    Work has commenced in this area, but is still in its
    infancy. Notable examples are:
    \cite{Letcher2019DifferentiableMechanics}, in which Letcher et
    al. consider the dynamics of Differentiable Games, though their
    focus is on its application to gradient descent in GANs as opposed
    to reinforcement learning, and \cite{Galstyan2013}, in which the
    dynamics of Q-Learning, with a Boltzmann action selection is
    considered. To achieve the result, the author replaces the
    strategy vector with a probability density function (pdf) over the
    strategy space, which leads to an integro-differential equation
    which describes the evolution of the pdf with time. Due to its
    complexity, the dynamics cannot be analysed as easily as those in
    \cite{Tuyls2006AnGames}, and so Galstyan restricts the analysis to
    the steady-state solution (i.e.~the fixed point) of the
    dynamics. Their analysis shows strong agreement with the designed
    experiments, under varying payoff conditions (note that the
    payoffs are now a function, rather than a discrete matrix).

@@

    \fr{application of the above?}

@@

    \fr{this last line might possibly be the most relevant for the CDT.}
